\pkg{dataMaid}: your assistant for data cleaning in \proglang{R}

### 2017-01-03 latex/article_vol2.tex
Rettes

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Anne H. Petersen, Claus Thorn Ekstr\o m} %% comma-separated
\Plaintitle{{dataMaid}: your assistant for data cleaning in R} %% without formatting
\Shorttitle{\pkg{dataMaid}: your data cleaning PA in R} %% a short title (if necessary)

@@

\subsubsection{Economic memory use} 
Another solution, which is especially relevant to Windows users due to
the unfortunate combination of memory control in this operating system
and RStudio, \hl{And also just R, right? Du har udkommenterert denne kommentar,
men jeg mener stadig at det er tilfældet, og jeg mener desuden ikke vi kan skrive 
det uden en præcision af hvad det går ud på. Hvad tænker du?}
is simply splitting the two steps performed
by \R{clean()}, namely producing the \pkg{rmarkdown} file and rendering it
afterwards. If the \R{rmarkdown} file is very long, as it will
typically be for very large datasets, keeping this file open in memory
wastes precious memory capacities. Therefore, we advice users to
instead split the two steps. This can be done in the following manner:

\begin{Schunk}
\begin{Sinput}
> clean(toyData, render = FALSE, openResult = FALSE}
> render("dataMaid_toyData.Rmd", quiet = FALSE)
\end{Sinput}
\end{Schunk}
This also deals with the fact that \pkg{dataMaid} can produce
\pkg{rmarkdown} files that supersedes the upper size limit. \hl{dette giver
ingen mening uden en præcision? "upper size limit" af hvad? Se udkommenteret 
kommentar.}
% of RStudio,
%which is currently \hl{find number} GBs (using RStudio version
%1.0.44). 
%\hl{Is this maybe too editor specific? On the other hand, a
%  lot of people do use RStudio...}.

>>>>

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Anne H. Petersen, Claus Thorn Ekstr\o m} %% comma-separated
\Plaintitle{{dataMaid}: your assistant for data cleaning in R} %% without formatting
\Shorttitle{\pkg{dataMaid}: your data cleaning personal assistant in R} %% a short title (if necessary)

@@

\subsubsection{Economic memory use} 
Another solution, which is especially relevant to Windows users due to
the unfortunate combination of memory control in this operating system
and \proglang{R}.
\hl{And also just R, right? Du har udkommenterert denne kommentar,
men jeg mener stadig at det er tilfældet, og jeg mener desuden ikke vi kan skrive 
det uden en præcision af hvad det går ud på. Hvad tænker du?}
is simply splitting the two steps performed
by \R{clean()}, namely producing the \pkg{rmarkdown} file and rendering it
afterwards. If the \R{rmarkdown} file is very long, as it will
typically be for very large datasets, keeping this file open in memory
wastes precious memory capacities. Therefore, we advice users to
instead split the two steps. This can be done in the following manner:

\begin{Schunk}
\begin{Sinput}
> clean(toyData, render = FALSE, openResult = FALSE}
> render("dataMaid_toyData.Rmd", quiet = FALSE)
\end{Sinput}
\end{Schunk}
This also deals with the fact that \pkg{dataMaid} can produce
\pkg{rmarkdown} files that supersedes the upper size limit of, say,
RStudio (which currently has an editor file size limit of 5MB). %\hl{dette giver
%ingen mening uden en præcision? "upper size limit" af hvad? Se udkommenteret 
%kommentar.}
% of RStudio,
%which is currently \hl{find number} GBs (using RStudio version
%1.0.44). 
%\hl{Is this maybe too editor specific? On the other hand, a
%  lot of people do use RStudio...}.
